Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-01 neurips-20/cvx-flats.tex
Missed a merge conflict resolution
Finished a pass over the main text except section 6.  Afraid to touch that one.

\bo{Reworded to avoid saying our findings are major -- some people won't like that.}\jessie{Good point}
Our results make two contributions to this field.
First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
This lets us use property elicitation to bound the minimum prediction dimension needed to construct a consistent convex surrogate.
Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
The bounds we show in our second contribution (Theorem~\ref{thm:cvx-flats}) are general enough to apply across all four settings, and is the first bound to our knowledge to handle this generality.
=======
Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.

@@

%\raf{I'd suggest discussing general stuff here ($\X\times\Y$, etc) and moving more specific stuff to a more contextual spot --- e.g. property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.  We could keep notation like $\supp,\affhull,2^\R$ in a terse paragraph just before 2.1}
\raf{Do we use $L(u;p)$ much?  It's $L(u,p)$ below.  I'd prefer to avoid it unless we really use it a ton.}\jessie{We primarily use $L(u;p)$. It was just a typo in this introduction of regret.  I don't mind changing it, but I like the semicolon.  I think that might be Bo's class influencing me haha.  My preferences aren't super strong one way of the other here.}

@@

\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
In discrete prediction tasks when given a target loss, the two are in fact equivalent.  
\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, it is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification. 
\cite{ramaswamy2016convex} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
\cite{steinwart2007compare} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, studying various classes of surrogate losses (i.e. margin-based, distance-based, supervised, unsupervised, etc.)
See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.

@@

\raf{I'd start off by motivating / explaining what all of these notions are trying to do, and perhaps fold in some related work discussion from above.  Like ``Various works have tried to quantify how difficult a learning problem is by determining the minimum dimension of a consistent surrogate loss...'' or similar.}\jessie{Attempted with the previous paragraph.}
\cite{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
Their convex calibration dimension results yield consistent surrogates for discrete prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
However, we show that Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and even derive tighter bounds on convex calibration dimension in some instances.

@@

\raf{It makes sense to discuss this here, but be a bit more precise with how they relate.  E.g. embedding is actually a special case of indirect elicitation.  You can say we show that calibration and indirect elic are equivalent for polyhedral losses, in the sense that if a polyhedral loss indirectly elicits a discrete loss, it is calibrated wrt that loss.  But we don't know exactly how ``convex elic complex'', ``embedding dimension'', ``polyhedral calibration dimension'', and ccdim relate.  Try to spell it out carefully, but briefly :-).  If too long, we can punt some of the discussion, especially the last bit on open questions, to the discussion.}\jessie{Attempted....}
\cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of indirect elicitation.
They show that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
Moreover,~\cite{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
Since embedding is a special case of indirect elicitation, there is a hierarchy of complexity notions in which embedding dimension $\preceq$ convex elicitation complexity and embedding dimension $\preceq$  ``polyhedral calibration dimension'' $\preceq$ convex calibration dimension.
However, it is an open problem to understand the tightness of this hierarchy.

@@

In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings (our four quadrants).
In discrete predictions, it is well-known that a surrogate is consistent with respect to a target loss if and only if it is calibrated with respect to the target (e.g.\,~\cite[Theorem 1, part 3]{bartlett2006convexity}).
We can show Theorem~\ref{thm:consistent-implies-indir-elic} through calibration (and even extend the definition of calibration to have meaning in continuous estimation), but calibration requires being given a target loss, which is not always guaranteed.
We delegate this proof to Appendix~\ref{app:calibration} when one is given a target loss and directly prove the general result, which does not rely on a target loss.
%This criterion is implied by both consistency and calibration, as fully explored in Appendix~\ref{app:calibration},
\raft{I really like the flow here, but was thinking of a slightly longer version of the nod to calibration.  Like ``You may be wondering if we could leverage ``consistency $\iff$ calibration'' to prove this.  We can, and can even extend that definition to a meaningful version for continuous predictions, but even this general calibration definition relies on a target loss being given.  We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''}
Since this criterion is implied by both consistency and calibration, it might be viewed as a weak necessary condition for existence of a consistent dimension-$d$ surrogate, yet it gives state-of-the-art lower bounds on $d$.
In particular, indirect elicitation bounds imply feasible subspace dimension bounds.

To begin, we formalize consistency in two ways to generalize across our four quadrants.
First, given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition \ref{def:consistent-ell}).
Second, given a property $\gamma$ (for example, the conditional mean), then we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.

@@

In an estimation task, rather than being given an original loss $\ell$, one may be given a property such as the expected value, variance, or entropy.
In this case, we formalize consistency as converging to the correct conditional estimates of the property.
Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$.
In particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.

@@

If $\gamma$ is an elicitable property, and is elicited by $\ell$, then the two definitions are equivalent when using excess expected loss as $\propdis$.
\begin{lemma}\label{lem:consistent-loss-implies-prop}
	Suppose we are given a surrogate loss $L$ and link $\psi$, and target loss $\ell$.
	Consider $\propdis: \R \times \simplex \to \reals_+$ with $\mu(r,p) := R_\ell(r,p)$.
	$(L, \psi)$ are consistent with respect to $\ell$ if and only if they are $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	First, observe that $\propdis(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p)$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.

@@

We now consider subgradients of convex losses and their flats in order to understand convex elicitation complexity. 
The intuition for this result comes from an observation about the existence of a set of witnesses in the Minkowski sum from the proof of~\cite[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
In fact, their main proof tool, the subspace of feasible dimensions (Definition~\ref{def:subspace-feas}), is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound}.
\raft{Reminder: give tons of credit to Hari's paper}

@@

When one is given a discrete target loss,~\cite{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
\begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
%  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
\end{definition}

We regain the bounds provided by~\cite[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. 
\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
%  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
  Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
  Now consider $v \in F - p$.
  Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the affine hull of $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
  In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
  Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
  Since level sets of elicitable properties are convex (\cite{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
  Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
%  
%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
%  Therefore, we have $v \in F - p \implies v \in \Sc_{\gamma_r}(p)$, so $(F - p) \subseteq \Sc_{\gamma_r}(p)$.
\end{proof}

The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\simplex}$.
\newcommand{\simplexp}{\Delta_{\Y'}}
\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
	Define $\gamma' : \simplex \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
	Then $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))$.
\end{lemma}
\begin{proof}
	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.

@@

Now consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}.
The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only move in the $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ directions without leaving the level sets respectively, and the three points are collinear in $\affhull(\simplex)$.  This yields $\ccdim(\ell^{abs}) \geq 3 - 1- 1 = 1$.
The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 3 - 1 - 1 = 1$ by the flat given by Theorem~\ref{thm:cvx-flats}.

>>>>

\bo{Reworded to avoid saying our findings are major -- some people won't like that.}\jessie{Good point}
Our results make two contributions to this field.
First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
This lets us use property elicitation to bound the minimum prediction dimension needed to construct a consistent convex surrogate.
Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
The bounds we show in our second contribution (Theorem~\ref{thm:cvx-flats}) are general enough to apply across all four settings, and is the first bound to our knowledge to handle this generality.

@@

%\raf{I'd suggest discussing general stuff here ($\X\times\Y$, etc) and moving more specific stuff to a more contextual spot --- e.g. property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.  We could keep notation like $\supp,\affhull,2^\R$ in a terse paragraph just before 2.1}
\raf{Do we use $L(u;p)$ much?  It's $L(u,p)$ below.  I'd prefer to avoid it unless we really use it a ton.}\jessie{We primarily use $L(u;p)$. It was just a typo in this introduction of regret.  I don't mind changing it, but I like the semicolon.  I think that might be Bo's class influencing me haha.  My preferences aren't super strong one way of the other here.}\jessie{Missing codim; in flats definition is fine?}

@@

\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} characterize consistent and calibrated surrogates for classification problems.
In discrete prediction tasks when given a target loss, the two are in fact equivalent.  
\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, it is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification. 
\cite{ramaswamy2016convex} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
\cite{steinwart2007compare} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, studying various classes of surrogate losses (i.e. margin-based, distance-based, supervised, unsupervised, etc.)
See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.

@@

\raf{I'd start off by motivating / explaining what all of these notions are trying to do, and perhaps fold in some related work discussion from above.  Like ``Various works have tried to quantify how difficult a learning problem is by determining the minimum dimension of a consistent surrogate loss...'' or similar.}\jessie{Attempted with the previous paragraph.}
\cite{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
Their convex calibration dimension results yield consistent surrogates for discrete prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
However, Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and sometimes derive even tighter bounds on convex calibration dimension.

@@

\raf{It makes sense to discuss this here, but be a bit more precise with how they relate.  E.g. embedding is actually a special case of indirect elicitation.  You can say we show that calibration and indirect elic are equivalent for polyhedral losses, in the sense that if a polyhedral loss indirectly elicits a discrete loss, it is calibrated wrt that loss.  But we don't know exactly how ``convex elic complex'', ``embedding dimension'', ``polyhedral calibration dimension'', and ccdim relate.  Try to spell it out carefully, but briefly :-).  If too long, we can punt some of the discussion, especially the last bit on open questions, to the discussion.}\jessie{Attempted....}
\cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of indirect elicitation.
They show that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
Moreover,~\cite{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
Since embedding is a special case of indirect elicitation, there is a hierarchy of complexity notions in which embedding dimension $\preceq$ convex elicitation complexity and embedding dimension $\preceq$  ``polyhedral calibration dimension'' $\preceq$ convex calibration dimension.
However, understanding the tightness of this hierarchy is an open problem.

@@

In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings (our four quadrants).
In discrete predictions, it is well-known that a surrogate is consistent with respect to a target loss if and only if it is calibrated with respect to the target (e.g.\,~\cite[Theorem 1, part 3]{bartlett2006convexity}).
We can show Theorem~\ref{thm:consistent-implies-indir-elic} through calibration (and even extend the definition of calibration to have meaning in continuous estimation), but calibration requires being given a target loss, which is not always guaranteed.
We delegate this proof to Appendix~\ref{app:calibration} when one is given a target loss and directly prove the general result, which does not rely on a target loss.
%This criterion is implied by both consistency and calibration, as fully explored in Appendix~\ref{app:calibration},
\raft{I really like the flow here, but was thinking of a slightly longer version of the nod to calibration.  Like ``You may be wondering if we could leverage ``consistency $\iff$ calibration'' to prove this.  We can, and can even extend that definition to a meaningful version for continuous predictions, but even this general calibration definition relies on a target loss being given.  We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''} \jessiet{Attempted to add some of this discussion}
Since this criterion is implied by both consistency and calibration, it might be viewed as a weak necessary condition for existence of a consistent dimension-$d$ surrogate, yet it gives state-of-the-art lower bounds on $d$.
In particular, indirect elicitation bounds imply feasible subspace dimension bounds.

We start by formalizing consistency in two ways that generalize across our four quadrants.
First, given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition \ref{def:consistent-ell}).
Second, given a property $\gamma$ (for example, the $\alpha$-quantile)\jessiet{changed example from conditional mean}, then we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.

@@

Instead of a target loss $\ell$, one may want to learn a property such as the expected value, variance, or entropy.
In this case, we formalize consistency as converging to the correct conditional estimates of the property.
Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$.
In particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.

@@

If $\gamma$ is an elicitable property, and is elicited by $\ell$, then the two definitions are equivalent when using target regret as $\propdis$.
\begin{lemma}\label{lem:consistent-loss-implies-prop}
	Suppose we are given a surrogate loss $L$ and link $\psi$, and target loss $\ell$.
	Consider $\propdis: \R \times \simplex \to \reals_+$ with $\mu(r,p) := R_\ell(r,p)$.
	$(L, \psi)$ are consistent with respect to $\ell$ if and only if they are $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	First, observe that $\propdis(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p)$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.

@@

We now consider subgradients of convex losses and their flats in order to understand convex elicitation complexity. 
The intuition for this result comes from an observation about the existence of a set of witnesses in the Minkowski sum from the proof of~\cite[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
In fact, their main proof tool, the subspace of feasible dimensions (Definition~\ref{def:subspace-feas}), is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound}.
\raft{Reminder: give tons of credit to Hari's paper}\jessiet{Attempted.}

@@

When given a discrete target loss,~\cite{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now.}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
\begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
%  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
\end{definition}

We regain the bounds provided by~\cite[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. \jessiet{Going to suggest proof to appendix.}
\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
%  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
  Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
  Now consider $v \in F - p$.
  Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the affine hull of $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
  In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
  Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
  Since level sets of elicitable properties are convex (\cite{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
  Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
%  
%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
%  Therefore, we have $v \in F - p \implies v \in \Sc_{\gamma_r}(p)$, so $(F - p) \subseteq \Sc_{\gamma_r}(p)$.
\end{proof}

The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\simplex}$.\jessiet{Going to suggest entire lemma to appendix.}
\newcommand{\simplexp}{\Delta_{\Y'}}
\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
	Define $\gamma' : \simplex \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
	Then $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))$.
\end{lemma}
\begin{proof}
	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.

@@

Now consider the distribution $q = (1/4, 1/4, 1/2)$, shown in blue in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}.
The feasible subspace dimension (of both $\gamma_\bot$ and $\gamma_3$) is $1$, since one only move toward the distributions $(0,1/2, 1/2)$ and $(1/2, 0, 1/2)$ without leaving the level sets, and the three points are collinear in $\affhull(\simplex)$.  This yields $\ccdim(\ell^{abs}) \geq 3 - 1- 1 = 1$.
The same line segment defines a flat contained in both $\gamma_\bot$ and $\gamma_3$, so we have $\ccdim(\ell^{abs}) \geq 3 - 1 - 1 = 1$ by the flat given by Theorem~\ref{thm:cvx-flats}.
